Estimation of Manning's Friction Coefficient using DART Buoys Data during \tohoku Tsunami

### 2014-01-07 paper/intro.tex
changes based on ibrahm comments

\section{Introduction}
\label{sec:intro}
Tsunamis in the past decade have been responsible for some of the most  deadly
and costly natural disasters ever recorded. Coastal communities  have faced this
hazard by assessing the risk they pose, attempting  to make informed decisions
about the likelihood that such an event would  occur with cost to life and
property.  To do this, computational models of  tsunami events are often
employed to explore multiple different scenarios to predict the water elevation
caused by the tsunamis. The accurate prediction  of water elevations, however, requires
accurate estimation of many model parameters that are either measured directly,
defined empirically, or estimated from a collection of observed data. Unfortunately,
since tsunami events are relatively rare,  there is an abundance of uncertainty
in the input data for these computational  models ranging from effects of the
domain such as bathymetry and friction parameterizations,  to the earthquake
source.  In this article, we aim to estimate the Manning's $n$ friction
coefficient. Our approach quantifies the uncertainty in the predicted water
elevation  and employs an inverse modeling approach to estimate the Manning's
$n$ coefficient using observations of water elevation measured during a tsunami event.

Previous work looking into uncertainty in the input for tsunami simulations
often has focused on the earthquake source but primarily as a way of
constraining the various proposed earthquake scenarios only after the event (see
for example \cite{MacInnes:2013cr}).  A similar approach for landslide-generated
tsunami was presented in Sarri \emph{et al.}, by building a statistical surrogate
using an emulator \cite{Sarri2012}. The implemented emulator was the Gaussian
process that requires using a combination of prior knowledge about the simulator
and appropriate choices of functions and parameters. Their work was presented as
a proof-of-concept case study where they only performed basic statistical and
sensitivity analysis.  Changes to the friction parameterization has been shown in 
the past to lead to significant changes to inundation levels \cite{Myers:2001el,Jakeman:2010hk} 
but these previous studies were limited in the scope of the changes to the parameterization allowed.  
In a recent work, Mayo et el. reformulated a statistical data assimilation method
generally used in the estimation of model states to estimate the Manning's $n$
coefficient~\cite{Mayo2013}. They used a low-dimensional representations of
Manning's $n$ coefficients and recovered it by assimilating synthetic water elevation data.

In this work, we focus our attention on the uncertainty in the friction
parameterization used in tsunami simulations. We present a three-dimensional 
representation of Manning's $n$ coefficient and an efficient method
to estimate this representation using real water elevation data. The method proposed here utilizes recent 
developments in Uncertainty Quantification (UQ) methods that allow 
probing of the sensitivity of realistic tsunami  models to uncertain parameters
without modifying the forward model and inferring those parameters
from a number of observations.  In particular, we implement an inverse modeling
approach that relies on the Bayesian inference technique.  We also employ
Polynomial Chaos (PC) expansions to construct a faithful surrogate model of the
response of the large and complex geophysical model simulations.  The
construction of the surrogate enables us to efficiently implement the Bayesian
inference technique as it dramatically reduces the cost of sampling the
posterior distribution.

PC expansions have been developed and applied in the engineering community to
quantify uncertainties in numerical simulations.  The main advantage of
using PC expansions is the ability of propagating input uncertainties through 
large, complex and non-linear models to compute the corresponding output uncertainties. 
Several researchers have been investigating the applicability of PC expansions for 
UQ in oceanic simulations~\citep{thacker2012,ashwanth2010,Alexanderian2012}. 
Recently, PC was combined with Bayesian inference to estimate the drag coefficient 
using temperature data collected during Typhoon Fanapi 2010. The same problem was 
solved using two different techniques: the adjoint method and Markov Chain Monte Carlo
(MCMC)\cite{sraj:2013a,sraj:2013b}.

In this work, we follow a similar procedure as in \cite{sraj:2013a,sraj:2013b}
to estimate Manning's $n$ coefficient using the \tohoku tsunami
event as a case-study. The quantity of interest is taken to be the surface
elevation $\eta$ and is compared to the available NOAA Deep-ocean Assessment and
Reporting Tsunamis (DART) buoys.  The forward model runs are performed using the
\geoclaw package following the setup in MacInnes \emph{et al.} including the
source models analyzed there \cite{MacInnes:2013cr}.

The structure of this manuscript is as follows. First, we discussing the uncertainties 
of the Manning'g $n$ coefficient to motivate the UQ problem in Section~\ref{sec:manning}
and present a proposed three-dimensional representation of $n$. 
In Section~\ref{sec:tohoku}, we describe our case-study the \tohoku tsunami,
summarize the forward simulations setup and present the DART buoys observational data. 
Section~\ref{sec:formu} describes the two main numerical methods employed in the UQ analysis:
Bayesian inference formalism that brings together observations 
and model results (briefly described in Section~\ref{sec:inference}) 
and PC expansions that were used to build the surrogate model (described
in Section~\ref{sec:uqpce}). Section~\ref{sec:results} describes the main results in 
three subsections: first, we perform error and convergence studies
as evidences that the PC surrogate is a faithful 
representation of the \geoclaw model; second, we use the PC surrogate to 
perform a statistical analysis and compute the  sensitivity of simulated water elevations
to the uncertain input parameters; and third, we present the result of the
posterior distributions obtained using Bayesian inference by MCMC. A discussion of our findings and methodology is finally presented in Section~\ref{sec:conc}.

>>>>

\section{Introduction}
\label{sec:intro}
Tsunamis in the past decade have been responsible for some of the most  deadly
and costly natural disasters ever recorded. Coastal communities  have faced this
hazard by assessing the risk they pose, attempting  to make informed decisions
about the likelihood that such an event would  occur with cost to life and
property.  Toward this goal, computational models of  tsunami events are often
employed to explore multiple different scenarios to predict the water elevation
caused by the tsunamis. The accurate prediction  of water elevations, however, requires
accurate estimation of many model parameters that are either measured directly,
defined empirically, or estimated from a collection of observed data. Unfortunately,
since tsunami events are relatively rare,  there is an abundance of uncertainty
in the input data for these computational  models ranging from effects of the
domain, such as bathymetry and friction parameterizations,  to the earthquake
source.  In this study, we aim to estimate the Manning's $n$ friction
coefficient \alert{add a sentence here about the Manning Coeff}. 
We aim at quantifying the uncertainty in the predicted water
elevation  and employs a Bayesian inverse modeling approach to estimate the Manning's
$n$ coefficient using observations of water elevation measured during a tsunami event.

Previous works looking into uncertainty in the input for tsunami simulations
focused on the earthquake source but primarily as a way of
constraining the various proposed earthquake scenarios only after the event (see
for example \cite{MacInnes:2013cr}).  A similar approach for landslide-generated
tsunami was presented in Sarri \emph{et al.}~\cite{Sarri2012}, by building a statistical surrogate
using an emulator. The implemented emulator was based on a Gaussian
process that requires using a combination of prior knowledge about the simulator
and appropriate choices of functions and parameters. Their work was presented as
a proof-of-concept case study where they only performed basic statistical and
sensitivity analysis.  Changes to the friction parameterization has been shown in 
the past to lead to significant changes to inundation levels \cite{Myers:2001el,Jakeman:2010hk}, 
but these previous studies \comment{were limited in the scope of the changes to the parameterization allowed}.  
In a recent work, Mayo \emph{et al.}~\cite{Mayo2013} reformulated a statistical data assimilation method
generally used in the estimation of model states to estimate the Manning's $n$
coefficient. They used a low-dimensional representations of
Manning's $n$ coefficients and recovered it by assimilating synthetic water elevation data
in a storm surge setting.

In this work, we focus our attention on the uncertainty in the friction
parameterization used in tsunami simulations. We present a three-dimensional 
representation of Manning's $n$ coefficient and an efficient method
to estimate this representation using real water elevation data. The method proposed here 
is based on recent developments in Uncertainty Quantification (UQ) methods that allow 
probing of the sensitivity of realistic tsunami  models to uncertain parameters
without modifying the forward model and inferring those parameters
from a number of observations.  In particular, we implement an inverse modeling
approach that relies on the Bayesian inference technique.  We resort to
Polynomial Chaos (PC) expansions to construct a faithful surrogate model of the
response of the large and complex geophysical model simulations \comment{ref on pcs}.
The construction of the surrogate enables us to efficiently implement the Bayesian
inference technique as it dramatically reduces the cost of sampling the
posterior distribution.

PC expansions have been developed and applied in the engineering community to
quantify uncertainties in numerical simulations.  The main advantage of
using PC expansions is the ability of propagating input uncertainties through 
large, complex and non-linear models leading to the corresponding output uncertainties. 
Several studies already investigated the efficiency of PC expansions for 
UQ in oceanic simulations~\citep{thacker2012,ashwanth2010,Alexanderian2012}. 
Recently, PC was combined with Bayesian inference to estimate the wind drag coefficient 
using temperature data collected during Typhoon Fanapi 2010. The same problem was 
solved using two different techniques: the adjoint method and Markov Chain Monte Carlo
(MCMC)\cite{sraj:2013a,sraj:2013b}.

In this work, we follow a similar procedure as in \cite{sraj:2013a,sraj:2013b}
to estimate Manning's $n$ coefficient using the \tohoku tsunami
event as a case-study. The quantity of interest is taken to be the surface
elevation $\eta$ and is compared to the available NOAA Deep-ocean Assessment and
Reporting Tsunamis (DART) buoys.  The forward model runs are performed using the
\geoclaw package following the setup in MacInnes \emph{et al.}~\cite{MacInnes:2013cr} including the
source models analyzed there.

The structure of this manuscript is as follows. First, we discuss the uncertainties 
of the Manning'g $n$ coefficient to motivate the UQ problem in Section~\ref{sec:manning}
and propose a three-dimensional representation of $n$. 
Section~\ref{sec:tohoku} describes our case-study, the \tohoku tsunami,
summarize the forward simulations setup, and present the DART buoys observational data. 
Section~\ref{sec:formu} presents the two main methods employed in the UQ analysis:
Bayesian inference that brings together observations 
and model results (Section~\ref{sec:inference}) 
and PC expansions that are used to build the surrogate model (Section~\ref{sec:uqpce}). Section~\ref{sec:results} describes the main results in 
three subsections: first, we perform error and convergence studies
as evidences that the PC surrogate is a faithful 
representation of the \geoclaw model; second, we use the PC surrogate to 
perform a statistical analysis and compute the  sensitivity of simulated water elevations
to the uncertain input parameters; and third, we present the results of the
posterior distributions obtained using Bayesian inference by MCMC. A discussion of our findings and methodology is finally presented in Section~\ref{sec:conc}.

### 2014-01-07 paper/pcstudy.tex
changes based on ibrahm comments

Figure~\ref{fig:rlzs} shows the evolution of the
water surface elevation predicted at the four different gauges 
using \geoclaw for the 125 different realizations 
required to compute the PC expansions. We notice that the 
variability in water surface elevation is insignificant for the first 
hour at all gauges as the plots of the different realizations superimpose.
Later in time, the variability starts to increase with time at the different gauges 
as indicated from the thickness of the bands formed by the plots of the realizations.
This variability appears to be significant at $t\sim$ 5400~s, 6000~s, 3600~s and 7200~s
for gauges 21401, 21413, 21418, 21419 respectively.
This is consistent with the distance from the gauge to the source of the earthquake
(epicenter located approximately 72 km east of \tohoku) where gauge 21418 is the closest and gauge 21419 is the farthest as shown in Figure~\ref{fig:setup_buoy_locations}.
The uncertainty in the prediction of water surface  elevation continues till the end of the simulations
at all gauges.

@@

A final check for the validity of the PC approximation 
consists of verifying whether the probability density
functions (pdfs) of water surface elevation at the different gauge locations
converges with increased order of the PC expansion.  Sample
water surface elevation pdfs are shown in Figure~\ref{fig:pdfs2}
and Figure~\ref{fig:pdfs3} where
the different curves correspond to increased order of PC ($p= 1-5$).
The plots indicate double peaked distributions that are
well-resolved with PC order $p=3$ at t = 7200 s as shown in Figure~\ref{fig:pdfs2}.
However, at t = 10800 s further refinement is needed as the pdfs are
sensitive to the refinement up to order $p=4$ but then becomes weakly 
insensitive with additional refinement  ($p = 5$) as indicated in Figure~\ref{fig:pdfs3}. 
We, therefore, used PC order $p = 5$ in all computations below.
This test and the various error metrics presented above provide confidence that the PC expansion is a faithful 
model surrogate that can be used in both the forward and inverse problems.

>>>>

Figure~\ref{fig:rlzs} plots the evolution of the
water surface elevation predicted at the four different gauges 
using \geoclaw for the 125 different realizations 
required to compute the PC expansions. We notice that the 
variability in water surface elevation is insignificant in the first 
hour at all gauges as the plots of the different realizations superimpose.
Later in time, the variability starts to increase at the different gauges 
as indicated from the thickness of the bands formed by the plots of the realizations.
This variability appears to be significant at $t\sim$ 5400~s, 6000~s, 3600~s and 7200~s
for gauges 21401, 21413, 21418, 21419, respectively.
This is consistent with the distance from the gauge to the source of the earthquake
(epicenter located approximately 72 km east of \tohoku) where gauge 21418 is the closest and gauge 21419 is the farthest as shown in Figure~\ref{fig:setup_buoy_locations}.
The uncertainty in the prediction of water surface  elevation persists till the end of the simulations
at all gauges.

@@

A final check for the validity of the PC approximation 
consists of verifying whether the probability density
functions (pdfs) of water surface elevation at the different gauge locations
converges with increased order of the PC expansion  \comment{add referece}.  Sample
water surface elevation pdfs are shown in Figure~\ref{fig:pdfs2}
and Figure~\ref{fig:pdfs3} where
the different curves correspond to increased order of PC ($p= 1-5$).
The plots indicate double peaked distributions that are
well-resolved with PC order $p=3$ at t = 7200 s as shown in Figure~\ref{fig:pdfs2}.
However, at t = 10800 s further refinement is needed as the pdfs are
sensitive to the refinement up to order $p=4$ but then becomes weakly 
insensitive with additional refinement  ($p = 5$) as shown in Figure~\ref{fig:pdfs3}. 
We, therefore, used PC order $p = 5$ in all computations below.
This test and the various error metrics presented above provide confidence that the PC expansion is a faithful 
model surrogate that can be used in both the forward and inverse problems.

### 2014-01-07 paper/tsunami.tex
Fix Manning's n formula coefficient
changes based on ibrahm comments

%!TEX root = paper.tex

@@

The \tohoku earthquake and tsunami of 2011 has been the subject of a number of
studies due to the wealth of observational evidence and severity of the tsunami.
The earthquake itself had an estimated magnitude of $\text{M}_\text{w}$ 9.0 and
caused massive devastation across Japan.  In the case study presented, the
simulation is based on work done in \cite{MacInnes:2013cr} and modified to use
the specified variable friction field. In this section we briefly describe the
forward computational model used, \geoclaw, the  simulation setup used in the
uncertainty analysis and finally describe the observations from NOAA DART buoys.

\subsection{\geoclaw} \label{ssub:geoclaw}
The \geoclaw software package uses a finite volume, wave-propagation approach described in \cite{LeVeque:1997eg} to solve the two-dimensional shallow water equations:
\begin{equation} \label{eq:swe}
    \begin{aligned}
    &\pd{}{t} h + \pd{}{x} (hu) + \pd{}{y} (hv) = 0, \\
    &\pd{}{t}(hu) + \pd{}{x} \left(hu^2 + \frac{1}{2} g h^2 \right ) + \pd{}{y} (huv) = ~~ fhv - gh \pd{}{x} b - C_f |\vec{u}| hu \\
    &\pd{}{t} (hv) + \pd{}{x} (huv) + \pd{}{y} \left (hv^2 + \frac{1}{2} gh^2 \right) = -fhu - gh \pd{}{y} b - C_f |\vec{u}| hv
    \end{aligned}
\end{equation}
where $h$ is the depth of the water column, $u$ and $v$ the velocities in the 
longitudinal and latitudinal directions respectively, $g$ the acceleration due 
to gravity, $b$ the bathymetry, $f$ the Coriolis parameter, and $C_f$ the bottom 
friction coefficient.  As is common in tsunami modeling, $C_f$ is calculated 
given a Manning's $n$ parameterization such that:
\begin{equation}
    C_f = \frac{g n^2}{h^{5/3}}
\label{eq:coef}
\end{equation}
where $n$ is an empirically determined parameter known as Manning's $n$.

The primary computational kernel in \geoclaw is the evaluation of the solution to the Riemann problem at each grid cell interface.  The Riemann solver used includes the ability to handle inundation (wet-dry interfaces), well-balancing, even when the momentum is non-zero, and entropy corrections \cite{George:2008aa}.

\subsubsection{Adaptivity} \label{ssub:adaptivity}
One unique feature that \geoclaw has is the ability to adaptively refine the grids used for the computation essentially following a region of interest as time progresses (in this case, the disturbance in the surface height $\eta$).  \geoclaw implements these algorithms following \cite{Berger:1984ui,Berger:1998aa} and is described in detail in \cite{Berger:2011du} in the case of tsunami modeling.

@@

The observations used in this study are from the Deep-ocean Assessment and
Reporting of Tsunamis (DART) buoy system developed and maintained by the
National Oceanic and Atmospheric Administration (NOAA).  The purpose of the
network is to provide early-warning detection and forecasting of tsunami
propagation in the Pacific Ocean \cite{Milburn:1996wm}.  The DART buoys closest
to the earthquake source of the \tohoku tsunami were buoys 21401, 21413, 21418,
and 21419 whose locations are shown in Figure~\ref{fig:setup_buoy_locations} and
whose de-tided data for the event are shown in Figure~\ref{fig:setup_buoy_data}.
The time $t=0$ is set to be the start of the earthquake.  We can see that the
primary tsunami waves generated reach the gauges between 40 minutes and 2 hours
after the earthquake.  The large spikes later in time present in the data at
gauge 21418 are data anomalies and not subsequent tsunami waves.

@@

\section{Manning’s $n$ Friction Parameterization} \label{sec:manning}

Manning's $n$ law provides a relationship between the friction coefficient
\eqref{eq:coef} appearing in the shallow water equations \eqref{eq:swe}
governing tsunamis and the roughness parameter $n$.  This Manning's $n$
coefficient is variable that is highly spatial  and dependent on the surface
characteristics of the sea-floor.  The direct measurement of $n$ is therefore
impossible, instead, values are often assigned from tables that are empirically
estimated for common types of land that are determined from satellite images. As
a result, the Manning’s n coefficients used in tsunami models often contain
large amounts of uncertainty.

The uncertainty in the Manning's $n$ coefficient leads to uncertainties in the
predicted quantities of interest such as the water elevations and becomes a
health risk during tsunami events. In addition,  the prediction of these
quantities of interest are often highly sensitive to  the changes in these
uncertain parameters.  In MacInnes \emph{et al.} a Manning's $n$ coefficient of 0.025
was used except on the Sendai plane where 0.035 was used to account for pasture,
farmland and rice paddies.  In this work, we seek to quantify parametric
uncertainty namely due to the uncertainty in the roughness parameter $n$. To
this end, we characterize the roughness $n$ by three different parameters that
are varied in three different regions but are assumed constant in each region.
The three regions are as follows:  on-shore whose coefficient is denoted by
$n_1$, near- shore  denoted by $n_2$, and deep-water denoted by $n_3$. The three
regions are shown in Figure~\ref{fig:ceofs}. To carry out the uncertainty
quantification we have employed polynomial chaos expansions as used in
\cite{sraj:2013a,sraj:2013b}.  The method and its application to our problem is
described in Section~\ref{sec:uqpce}.  To represent the uncertainty in the
Manning's $n$ coefficients a uniform distribution was assumed as the prior where
$N$ was sampled in the interval $n \in [0.005-0.2]$.

>>>>

%!TEX root = paper.tex
\section{Manning’s $n$ Friction Coefficient} \label{sec:manning}

Manning's $n$ law provides a relationship between the friction coefficient
\eqref{eq:coef} appearing in the shallow water equations \eqref{eq:swe}
governing tsunamis and the roughness parameter $n$.  This Manning's $n$
coefficient varies spatially  and is dependent on the surface
characteristics of the sea-floor.  A direct measurement of $n$ is therefore
impossible, instead, values are often assigned from tables that are empirically
estimated for common types of land that are determined from satellite images. As
a result, the Manning’s n coefficients used in tsunami models often contain
large amounts of uncertainty.

The uncertainty in the Manning's $n$ coefficient leads to uncertainties in the
predicted quantities of interest such as the water elevations and becomes a
health risk during tsunami events. In addition,  the prediction of these
quantities of interest are often highly sensitive to changes in these
uncertain parameters.  In MacInnes \emph{et al.} a Manning's $n$ coefficient of 0.025
was used except on the Sendai plane where 0.035 was used to account for pasture,
farmland and rice paddies.  In this work, we seek to quantify parametric
uncertainty due to the uncertainty in the Manning's $n$ friction coefficient. To
this end, we characterize $n$ as being contasnt over three different 
regions. The three regions are:  on-shore whose coefficient is denoted by
$n_1$, near- shore  denoted by $n_2$, and deep-water denoted by $n_3$. The three
regions are shown in Figure~\ref{fig:ceofs}. To quantify the uncertainties
with respect to those three parameters we employ Polynomial Chaos (PC) expansions as used in
\cite{sraj:2013a,sraj:2013b}.  The method and its application to our problem is
described in Section~\ref{sec:uqpce}.  To represent the uncertainty in the
Manning's $n$ coefficients an uninformative uniform distribution was assumed as the prior with
$n$  sampled from the interval $n \in [0.005-0.2]$.

@@

The \tohoku earthquake and tsunami of 2011 has been the subject of a number of
studies due to the wealth of observational evidence and severity of the tsunami.
The earthquake itself had an estimated magnitude of $\text{M}_\text{w}$ 9.0 and
caused massive devastation across Japan.  In our case study, the
simulation is based on work done in \cite{MacInnes:2013cr} and modified to use
the specified variable friction field. Hereafter, we briefly describe the
forward computational model, \geoclaw, the  simulation setup used in the
uncertainty analysis, and finally present the observations from NOAA DART buoys.
\alert{describe a bit more the tsunami and its geophysical location}.
\subsection{\geoclaw} \label{ssub:geoclaw}
The \geoclaw software package uses a finite volume, wave-propagation approach as described in \cite{LeVeque:1997eg} to solve the two-dimensional shallow water equations:

\begin{equation} \label{eq:swe}
    \begin{aligned}
    &\pd{}{t} h + \pd{}{x} (hu) + \pd{}{y} (hv) = 0, \\
    &\pd{}{t}(hu) + \pd{}{x} \left(hu^2 + \frac{1}{2} g h^2 \right ) + \pd{}{y} (huv) = ~~ fhv - gh \pd{}{x} b - C_f |\vec{u}| hu, \\
    &\pd{}{t} (hv) + \pd{}{x} (huv) + \pd{}{y} \left (hv^2 + \frac{1}{2} gh^2 \right) = -fhu - gh \pd{}{y} b - C_f |\vec{u}| hv,
    \end{aligned}
\end{equation} 
where $h$ is the depth of the water column, $u$ and $v$ the velocities in the 
longitudinal and latitudinal directions respectively, $g$ the acceleration due 
to gravity, $b$ the bathymetry, $f$ the Coriolis parameter, and $C_f$ the bottom 
friction coefficient.  As is common in tsunami modeling, $C_f$ is calculated 
given a Manning's $n$ parameterization such that:

\begin{equation}
    C_f = \frac{g n^2}{h^{4/3}},
\label{eq:coef}
\end{equation}
where $n$ is an empirically determined parameter known as Manning's $n$.

The primary computational kernel in \geoclaw is the evaluation of the solution to the Riemann problem at each grid cell interface.  The Riemann solver used includes the ability to handle inundation (wet-dry interfaces), well-balancing, even when the momentum is non-zero, \alert{and entropy corrections} \cite{George:2008aa}.

%\subsubsection{Adaptivity} \label{ssub:adaptivity}
One unique feature that \geoclaw has is the ability to adaptively refine the grids used for the computation essentially following a region of interest as time progresses (in this case, the disturbance in the surface height $\eta$).  \geoclaw implements these schemes following \cite{Berger:1984ui,Berger:1998aa} and is described in detail in \cite{Berger:2011du} in the case of tsunami modeling.

@@

The observations used in this study are from the Deep-ocean Assessment and
Reporting of Tsunamis (DART) buoy system developed and maintained by the
National Oceanic and Atmospheric Administration (NOAA).  The purpose of the
network is to provide early-warning detection and forecasting of tsunami
propagation in the Pacific Ocean \cite{Milburn:1996wm}.  The DART buoys closest
to the earthquake source of the \tohoku tsunami were buoys 21401, 21413, 21418,
and 21419 whose locations are shown in Figure~\ref{fig:setup_buoy_locations} and
whose de-tided water surface elevation data for the event are shown in Figure~\ref{fig:setup_buoy_data}.
The time $t=0$ is set to be the start of the earthquake \comment{frequency of data}.  We can see that the
primary tsunami waves generated reach the gauges between 40 minutes and 2 hours
after the earthquake.  The large spikes later in time present in the data at
gauge 21418 are data anomalies and not subsequent tsunami waves.

@@
